---
title: "Lab 04 - La Quinta is Spanish for next to Denny's, Pt. 2"
author: "Jonathan Klus"
date: "21 September 2021"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
library(dsbox)
library(ggplot2)

knitr::opts_chunk$set(fig.width=unit(5,"cm"), fig.height=unit(3,"cm"))
```

```{r load-data, message = FALSE}
states = read_csv("data/states.csv")
```

### Exercise 0

```{r lintr-warm-up}

str_c("Here is an incredible, grandiloquent,", 
      "extreme, terrible, verbose, lengthy, awesome-in-the-original-sense,", 
      "no good and very long line (of code).")

better_variable_name = 0
this_is_a_bad_boolean = TRUE
needs_infix_spacing = 1 * 0^0
this = mtcars %>% 
  mutate(needs = mpg * wt) %>% 
  mutate(to_have = hp / cyl) %>%
  mutate(one = "pipe_step") %>% 
  mutate(per = "line")
```

### Exercise 1

```{r}
lint_assignment()
```

We get warnings about the pipe operator, spaces between infix operators, too many characters
on a given line, using T instead of TRUE as a boolean operator. 

### Exercise 2

```{r}
dn_ak = dennys %>%
  dplyr::filter(state == "AK")
nrow(dn_ak)
```

### Exercise 3

```{r}
lq_ak = laquinta %>%
  dplyr::filter(state == "AK")
nrow(lq_ak)
```

### Exercise 4

There are $2*3 = 6$ pairings between Denny's and La Quinta locations in Alaska. 

### Exercise 5

```{r}
dn_lq_ak = dplyr::full_join(dn_ak, lq_ak, by = "state")
dn_lq_ak
nrow(dn_lq_ak)
names(dn_lq_ak)
```


### Exercise 6

```{r load-haversine}
source("haversine.R")

# calculate distances
dn_lq_ak = dn_lq_ak %>%
  dplyr::mutate(distance = haversine(long1 = longitude.x, 
                                     lat1 = latitude.x,
                                     long2 = longitude.y,
                                     lat2 = latitude.y))
```

### Exercise 7

```{r}
dn_lq_ak_mindist = dn_lq_ak %>%
  dplyr::group_by(address.x) %>%
  dplyr::summarise(closest = min(distance))
dn_lq_ak_mindist
```
### Exercise 8

```{r}
summary(dn_lq_ak_mindist$closest)
ggplot2::ggplot(data = dn_lq_ak_mindist, aes(x = closest)) +
  ggplot2::geom_boxplot() + 
  ggplot2::xlab("Distance (km)") + 
  ggplot2::ggtitle("Distance from Denny's to Closest La Quinta in AK") + 
  ggplot2::theme_classic() +
  ggplot2::scale_y_continuous(breaks = NULL)
```

Since there are only three Denny's in the entire state of Alaska, we have only 
the distances from these Denny's to the closest La Quinta to summarize. The average
distance is 4.4 km, and the data are left skewed, with a median distance of 5.2 km.
The furthest one would need to travel from Denny's to the closest La Quinta in the 
state of Alaska is 6 km, while the closest is just over 2 km. 

### Exercise 9: New York

```{r}
lq_ny = laquinta %>%
  dplyr::filter(state == "NY")
nrow(lq_ny)

dn_ny = dennys %>%
  dplyr::filter(state == "NY")
nrow(dn_ny)

dn_lq_ny = dplyr::full_join(dn_ny, lq_ny, by = "state") %>% 
    dplyr::mutate(distance = haversine(long1 = longitude.x, 
                                       lat1 = latitude.x,
                                       long2 = longitude.y,
                                       lat2 = latitude.y)) %>%
    dplyr::group_by(address.x) %>%
    dplyr::summarise(closest = min(distance))

summary(dn_lq_ny$closest)
ggplot2::ggplot(data = dn_lq_ny, aes(x = closest)) +
  ggplot2::geom_boxplot() + 
  ggplot2::xlab("Distance (km)") + 
  ggplot2::ggtitle("Distance from Denny's to Closest La Quinta in NY") + 
  ggplot2::theme_classic() +
  ggplot2::scale_y_continuous(breaks = NULL)
```

There are 56 Denny's in the state of New York. The average from Denny's to La Quinta
is 33.6 km, and the data are right skewed, with a median distance of 24.2 km.
The furthest one would need to travel from Denny's to the closest La Quinta in the 
state of /New York is 99 km, while the closest is 1.3 km. In general, it does
not appear that La Quinta is Spanish for "Next to Denny's" in the great state of New York. 

### Exercise 10: Florida

```{r}
lq_fl = laquinta %>%
  dplyr::filter(state == "FL")
nrow(lq_fl)

dn_fl = dennys %>%
  dplyr::filter(state == "FL")
nrow(dn_fl)

dn_lq_fl = dplyr::full_join(dn_fl, lq_fl, by = "state") %>% 
    dplyr::mutate(distance = haversine(long1 = longitude.x, 
                                       lat1 = latitude.x,
                                       long2 = longitude.y,
                                       lat2 = latitude.y)) %>%
    dplyr::group_by(address.x) %>%
    dplyr::summarise(closest = min(distance))

summary(dn_lq_fl$closest)
ggplot2::ggplot(data = dn_lq_fl, aes(x = closest)) +
  ggplot2::geom_boxplot() + 
  ggplot2::xlab("Distance (km)") + 
  ggplot2::ggtitle("Distance from Denny's to Closest La Quinta in FL") + 
  ggplot2::theme_classic() +
  ggplot2::scale_y_continuous(breaks = NULL)
```

There are 140 Denny's in the state of Florida. The average from Denny's to La Quinta
is 13.5 km, and the data are right skewed, with a median distance of 8.7 km.
The furthest one would need to travel from Denny's to the closest La Quinta in the 
state of /New York is 176.5 km, while the closest is 0.04 miles. In general, it does
seems that the distance between the closest Denny's and La Quinta in Florida is extremely
small (essentially "next to" each other), while the furthest are separated by nearly
200 miles. The vast majority of pairs are within 15 miles of each other, since the 75th
percentile is 15.3. So while not literally next to each other, most Denny's in Florida
are quite close to a La Quinta. 

### Exercise 11

Based on our limited analysis above, it seems that Mitch Hedberg's joke is most 
likely to hold true in states that have large numbers of Denny's (i.e. FL, TX, CA) 
and large numbers of La Quinta hotels. In states with smaller numbers of these establishments (like
NY, NC, etc.) the distance from the nearest La Quinta to the nearest Denny's tend 
to be farther than in states like Florida, which have many more Denny's restaurants. 
It makes sense that the more Denny's locations a state has, the more likely one
would be to fall within close distance to a La Quinta hotel. 

```{r}
dennys %>% 
  group_by(state) %>% 
  summarize(n = n()) %>%
  arrange(desc(n))

laquinta %>% 
  group_by(state) %>% 
  summarize(n = n()) %>%
  arrange(desc(n))
```

