---
title: "Lab 04 - La Quinta is Spanish for next to Denny's, Pt. 2"
author: "Insert your name here"
date: "Insert date here"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
library(dsbox)
```

```{r load-data, message = FALSE}
states = read_csv("data/states.csv")
```

### Exercise 0

```{r lintr-warm-up}
print("Here is an incredible, extreme, terrible, exceptional, great, impressive, awesome, no good, very long line in a code chunk.")
Bad.Variable.Name = 0
bad_boolean = T
bad_spacing=sqrt(4*4)
```


### Exercise 1

Remove this text, and add your answer for Exercise 1 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 2

Remove this text, and add your answer for Exercise 1 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 3

...

### Exercise 4

Here is an incredibly, extremely, terribly, exceptionally, greatly, impressively, awesomely, no good, very long line in the prose.



### Exercise 5

```{r load-haversine}
source("haversine.R")
```

...Add chunks and description for Ex 5.

### Exercise 6

...

Add exercise headings as needed.
