---
title: "Lab 04 - La Quinta is Spanish for next to Denny's, Pt. 2"
author: "Insert your name here"
date: "Insert date here"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse)
library(dsbox)
```

```{r load-data, message = FALSE}
states = read_csv("data/states.csv")
```

### Exercise 0

```{r lintr-warm-up}
str_c("Here is an incredible, grandiloquent,", "extreme, terrible, verbose, lengthy, awesome-in-the-original-sense,", "no good and very long line (of code).")
Bad.Variable.Name = 0
this_is_a_bad_boolean = T
needs_infix_spacing=1*0^0
this = mtcars %>% mutate(needs = mpg * wt) %>% mutate(to_have = hp / cyl) %>%
  mutate(one = "pipe_step") %>% mutate(per = "line")
```

### Exercise 1

Remove this text, and add your answer for Exercise 1 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 2

Remove this text, and add your answer for Exercise 1 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 3

...

### Exercise 4

...


### Exercise 5


### Exercise 6

```{r load-haversine}
source("haversine.R")
```

...Add additional chunks and description for Ex 6 as needed.

...

Add more exercise headings, chunks, etc, as needed.
